### 2016-02-18 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Uniformized a lot of figures, styles, ...

The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
\TODO{ordos are incorrect: notation-wise}
\begin{align}\label{lpmGTaylorS}
G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
\bigO{\left(\frac{r}{N}\right)^{(R+1)}},
\\
\label{lpmTTaylorS}
T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
\bigO{  \left(\frac{r}{N}\right)^{(R+1)}  }
,
\\
\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
\end{align}

>>>>

The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
\begin{align}\label{lpmGTaylorS}
G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
\bigO{\left(\frac{r}{N}\right)^{R+1}},
\\
\label{lpmTTaylorS}
T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
\bigO{  \left(\frac{r}{N}\right)^{R+1}  }
,
\\
\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
\end{align}

### 2016-02-18 ch05-initvals/initial-values.tex
Uniformized a lot of figures, styles, ...

An implementation of the \gls{RFIR} estimator is available as the \code{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \code{arxoptions}. 
The hyperparameters can be determined via \code{arxregul}.
More information about the \gls{RFIR} estimator can be found in
~\citep{Pillonetto2010,Chen2012}. 
The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
\end{enumerate}

@@

\begin{remark}
Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the \gls{FRF}. 
A corresponding parametric estimate is obtained as follows. 
A parametric estimator (GTLS, BTLS, and MLE) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated FRF, with the transient term $I$ set to zero. 
It is important to note that invoking the GTLS, BTLS and MLE on the FRFs from methods 3) and 4) will yield a different result from applying the GTLS, BTLS and MLE on the raw data. This is because the FRFs from 3) and 4) have been smoothed and, thus, have a significantly lower noise variance.
\TODO{spectra als formule geven}
\end{remark}
%}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}[p]
  \centering
  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
% \input{\thisDir/table2.tex}

\pgfplotstabletypeset[precision=2,zerofill=true]{
method              P000      P025      P050        P075     P100   
\model{VXI}         0.47325   0.916589   1.06396   1.29177   2.4089
\model{exist}       1.48252   1.88392   13.7177   19.3113   26.7984
\model[init]{trunc} 1.35399   2.72412   14.9431   24.7154   85.3351
\model{trunc}       1.27344   1.71872    2.34574  13.0301   63.8373
\model[init]{RFIR}  1.10525   1.61051    1.7778    2.00318  18.211
\model{RFIR}        1.20554   1.57398    1.72416   1.84941   4.55004
\model{best}        1.20554   1.55725    1.72059   1.84593  15.0063
}
\label{tbl:validationMeasurements}
\end{table}

>>>>

An implementation of the \gls{RFIR} estimator is available as the \code{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \code{arxoptions}. 
The hyperparameters can be determined via \code{arxregul}.
More information about the \gls{RFIR} estimator can be found in
~\citep{Pillonetto2010,Chen2012}. 
The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the \gls{FRF}.
\end{enumerate}

@@

\begin{remark}
Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the \gls{FRF}. 
A corresponding parametric estimate is obtained as follows. 
A parametric estimator (\gls{GTLS}, \gls{BTLS}, and \gls{MLE}) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated \gls{FRF} $G_{\bullet}(\omega_k)$, with the transient term $I$ set to zero:
\begin{equation}
  U_{\mathrm{FRF}}(\omega_k) \isdef 1 
  \qquad \text{and} \qquad
  Y_{\mathrm{FRF}}(\omega_k)  \isdef G_{\bullet}(\omega_k)
  \text{.}
\end{equation}
It is important to note that invoking the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the \glspl{FRF} from methods 3) and 4) will yield a different result from applying the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the raw data. 
This is because the \glspl{FRF} from 3) and 4) have been smoothed and, thus, have a significantly reduced noise variance.
\end{remark}
%}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}[p]
  \centering
  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
% \input{\thisDir/table2.tex}
\pgfplotstabletypeset[zerofill=true,precision=2]{
method              P000      P025      P050        P075     P100   
\model{VXI}         0.47325   0.916589   1.06396   1.29177   2.4089
\model{exist}       1.48252   1.88392   13.7177   19.3113   26.7984
\model[init]{trunc} 1.35399   2.72412   14.9431   24.7154   85.3351
\model{trunc}       1.27344   1.71872    2.34574  13.0301   63.8373
\model[init]{RFIR}  1.10525   1.61051    1.7778    2.00318  18.211
\model{RFIR}        1.20554   1.57398    1.72416   1.84941   4.55004
\model{best}        1.20554   1.55725    1.72059   1.84593  15.0063
}
\label{tbl:validationMeasurements}
\end{table}

### 2016-02-18 config/styles.inc.tex
Uniformize formatting a bit
Uniformized a lot of figures, styles, ...

\def\thisDir{.}

@@

\pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
\pgfplotsset{bw/.style={fill=bwfill,draw=bwline}}
\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=0.75pt}}

@@

\pgfplotsset{percentileLines/.style={black,dashed}}

\tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}

%% TABLE STYLES

\pgfplotstableset{
	%zerofill=true,
	after row=[3pt],
	assign column name/.code={%
        \pgfkeyssetvalue{/pgfplots/table/column name}{\multicolumn{1}{c}{\multirow{2}{*}{#1}} }%
    },
	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}}, 
	columns/contribution/.style={column name={\textsc{Contribution}}},
	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
	columns/P025/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$25\%$}}}},
	columns/P050/.style={column type=r,column name={\shortstack[r]{\textsc{Median}\\{$50\%$}}}},
	columns/P075/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$75\%$ }}}},
	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
	postproc cell content/.append code={
            %\ifnum1=\pgfplotstablepartno
                \pgfkeysalso{@cell content/.add={}{\%}}%
            %\fi
        },
	},
	every head row/.style={before row=\toprule, after row={\\\midrule}},
    every last row/.style={after row=\bottomrule}
}

>>>>

% \def\thisDir{.}

@@

\pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,area legend}}
\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=0.75pt}}

@@

\pgfplotsset{percentileLines/.style={black,dashed}}
\tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}

%% TABLE STYLES
% http://tex.stackexchange.com/questions/83487/pgfplotstable-converting-zeros-to-in-a-knitr-inline-table

\pgfplotstableset{
	%zerofill=true,
	after row=[3pt],
         every head row/.style={before row=\toprule, after row={\\\midrule}},
         every last row/.style={after row=\bottomrule},
	assign column name/.code={%
        \pgfkeyssetvalue{/pgfplots/table/column name}{\multicolumn{1}{c}{\multirow{2}{*}{#1}} }%
    },
	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}}, 
	columns/contribution/.style={column name={\textsc{Contribution}}},
	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
	columns/P025/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$25\%$}}}},
	columns/P050/.style={column type=r,column name={\shortstack[r]{\textsc{Median}\\{$50\%$}}}},
	columns/P075/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$75\%$ }}}},
	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
	postproc cell content/.append code={
            %\ifnum1=\pgfplotstablepartno
                \pgfkeysalso{@cell content/.add={}{\%}}%
            %\fi
        },
	}
}
